Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 b

### 2018-06-06 ms.tex
updated description of photometry.

\begin{deluxetable}{lrr}
\tablecaption{List of observations}\label{tab:photSummary}
\tablewidth{0pt}
\tablehead{
\colhead{Date} &
\colhead{Weather} &
\colhead{Amplitude} \\
\colhead{UT} & & \\
 }
\startdata
2016-06-10 & Clouds	& \nodata \\
2016-06-12 & Clear 		& 0.94 $\pm$ 0.16 \\
2016-06-14 & Clear 		&0.70 $\pm$ 0.18\\
2016-07-12 & Clear 		& 0.78 $\pm$ 0.14 \\
2016-07-14 & Mostly clear	& 1.33 $\pm$ 0.14 \\
2016-07-16 & Clear 		& 2.14 $\pm$ 0.19 \\
\enddata
\tablenotetext{}{Summary of observations and conditions in this work.}
\end{deluxetable}

\section{Observations}
We observed \sha\ with the Mont4k imager on the 61-inch Kuiper observatory located on Mt Bigelow, Arizona on UT dates 2016-06-12, 2016-06-14, 2016-07-12, 2016-07-14, 2016-07-16.
On all nights we used 90 second exposures using a Harris-R filter to best approximate the $r'$ filter used in \citet{schlawin2016kic1255}.
The nights were clear with the exception of a few passing clouds on 2016-07-14.
We also attempted photometry on 2016-06-10, but clouds prevented precision time series.
Table \ref{tab:photSummary} shows a summary of our observations and the UT dates.
The data was taken in a 3x3 binning mode resulting in an effective 0.43"/pixel plate scale.
We used a photometric aperture of 9 pixels (3.9") and a background annulus from 9 to 12 pixels (3.9" to 5.2") on all stars and nights.

@@

For the photometric reduction, we used the \texttt{ccdproc} package to generate master flat field and bias files.
They were combined with an average with a low threshold of 2$\sigma$ and a high threshold of 5$\sigma$.
12 stable reference stars with similar R band brightnesses were used to construct a reference time series to correct for variable telluric and instrument throughput.
The reference stars are identified in Figure \ref{fig:refStars}.
These 12 reference stars' time series were combined with a weighted average and this combined time series was divided into the target, \sha.

For the photometric reduction, we used the \texttt{ccdproc} package to generate master flat field and bias files.
We combined the flat fields and bias files with a a sigma-clipped average with a low threshold of 2$\sigma$ and a high threshold of 5$\sigma$.

\begin{figure}
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/ut2016_07_14_clouds/figure_index_152.pdf}
\includegraphics[width=0.49\textwidth]{images/stamps_kic1255_UT2016_07_14.pdf}
\caption{Target (src) and reference stars (numbered) used on UT 2016-07-14.
The reference stars were chosen to have similar count levels as the source. 
}\label{fig:refStars}
\end{centering}
\end{figure}

@@

\software{astropy \citep{astropy2013}, 
	\texttt{scikit-learn} \citep{pedregosa2011scikit-learn},
	\texttt{iraf},
	\texttt{SpecMatch-Emp} \citep{yee2017specMatch} 
          %\texttt{emcee} \citep{foreman-mackey2013emcee}, 
          }

>>>>

\begin{deluxetable}{lrr}
\tablecaption{List of photometric observations}\label{tab:photSummary}
\tablewidth{0pt}
\tablehead{
\colhead{Date} &
\colhead{Weather} &
\colhead{Amplitude} \\
\colhead{UT} & & \\
 }
\startdata
2016 Jun 10 & Clouds	& \nodata \\
2016 Jun 12 & Clear 		& 0.94 $\pm$ 0.16 \\
2016 Jun 14 & Clear 		&0.70 $\pm$ 0.18\\
2016 Jul 12 & Clear 		& 0.78 $\pm$ 0.14 \\
2016 Jul 14 & Mostly clear	& 1.33 $\pm$ 0.14 \\
2016 Jul 16 & Clear 		& 2.14 $\pm$ 0.19 \\
\enddata
\tablenotetext{}{Summary of the attempted photometric observations of \shStar\ with the 61-inch Kuiper observatory.}
\end{deluxetable}

\section{Observations}
We attempted to observe 6 transit events of \sha\ with the Mont4k imager on the 61-inch Kuiper observatory located on Mt Bigelow, Arizona on UT using the f/13.5 Cassegrain focus.
On all nights we used 90 second exposures using a Harris-R filter to best approximate the $r'$ filter used in \citet{schlawin2016kic1255}.
5 of the 6 nights were clear with the exception of a few passing clouds on UT 2016 Jul 14.
Cloudy skies on UT 2016 Jun 10 that prevented high precision time series.
Table \ref{tab:photSummary} shows a summary of our observations and the UT dates.
The data was taken in a 3x3 binning mode resulting in an effective 0.43"/pixel plate scale.

@@

For the photometric reduction, we used the Python \texttt{ccdproc} package \citep{craig2015ccdproc} to generate master flat field and bias files.
They were combined with an average with a low threshold of 2$\sigma$ and a high threshold of 5$\sigma$.

We used the \texttt{photutils v0.3} \citep{bradley2016photutilsv0p3} package to centroid and extract fluxes of the \shStar\ and the reference stars.
We used a photometric aperture of 9 pixels (3.9") and a background annulus from 9 to 12 pixels (3.9" to 5.2") on all stars and nights.
12 stable reference stars with similar R band brightnesses were used to construct a reference time series to correct for variable telluric and instrument throughput.
The reference stars are identified in Figure \ref{fig:refStars}.
These 12 reference stars' time series were combined with a weighted average and this combined time series was divided into the target, \shStar.

\begin{figure}
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/ut2016_07_14_clouds/figure_index_152.pdf}
\includegraphics[width=0.49\textwidth]{images/stamps_kic1255_UT2016_07_14.pdf}
\caption{{\it Left:} \shStar\ (src) and reference stars (numbered) used on UT 2016-07-14 are shown over the full 9.8\arcmin $\times$ 9.8\arcmin\ Field of View of Mont4K.
{\it Right:} Postage stamp zoom-ins for the source and reference stars show the point spread functions for each star.
The reference stars were chosen to have similar count levels as \shStar.
}\label{fig:refStars}
\end{centering}
\end{figure}

@@

\software{
	\texttt{ccdproc} \citep{craig2015ccdproc},
	\texttt{astropy} \citep{astropy2013}, 
	\texttt{scikit-learn} \citep{pedregosa2011scikit-learn},
	\texttt{photutils v0.3} \citep{bradley2016photutilsv0p3},
	\texttt{iraf},
	\texttt{SpecMatch-Emp} \citep{yee2017specMatch} 
          %\texttt{emcee} \citep{foreman-mackey2013emcee}, 
          }
